Bootstrapping Multi-atlas Hippocampal Segmentation with MAGeT

### 2013-03-07 paper.Rnw
Move movement on the results

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1 X-Validation Dataset Demographics Table
%
<<ADNI-Xval-demographics, echo=F, results="asis",cache=FALSE>>=
adni_69_RIDs = c("295","413","619","685","729","782","938","954",
                 "1018","1155","907","981","222","324","448","546",
                 "553","572","602","610","814","1341","675","681",
                 "731","1130","41","68","70","101","249","293","316",
                 "414","698","1206","1222","1339","751","1030","3",
                 "5","10","16","22","53","168","183","241","1205",
                 "328","1095","991","213","159","337","343","642",
                 "753","1109","1217","29","56","1188","1293","149",
                 "382","431","1202")
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 +
               MMSE, data = adnimerge, subset = VISCODE == 'bl' & RID %in%
               adni_69_RIDs, method = "reverse", test=FALSE, overall=TRUE)

@@

{\bf Atlas and template libary.} The Winterburn atlases were used as the atlas
library.  The template library consisted of 21 randomly selected images from the
ADNI1 data dataset (7 healthy, MCI and AD subjects).

@@

@@

@@

<<ADN1-Xval_prep, include=FALSE>>=

# all data from the validation trials
t_data       = read.csv(gzfile('data/a2a_ants/results_2013_01_03.csv.gz'))
t_data       = subset(t_data, atlases %in% c(1,3,5,7,9))
a_data       = t_data[,] #read.csv(gzfile('data/a2a_tracc/results_2013_01_03.csv.gz'))
diagnoses    = read.csv('data/a2a_diagnoses.csv')
t_data$se    = NULL
t_data$sn    = NULL
t_data$j     = NULL
a_data$se    = NULL
a_data$sn    = NULL
a_data$j     = NULL       
# add registration method to data frames (before joining)
t_data       = cbind(t_data, reg_method = "ANIMAL")
a_data       = cbind(a_data, reg_method = "ANTS")

# baseline is multi-atlas majority vote (even though we have MA with other methods)
t_ma = subset(t_data, approach=="multiatlas" & method=="majvote")
a_ma = subset(a_data, approach=="multiatlas" & method=="majvote")
t_mb = subset(t_data, approach=="mb")
a_mb = subset(a_data, approach=="mb")

ma = rbind(t_ma,a_ma)
mb = rbind(t_mb,a_mb)
ma$templates =  ma$atlases  # since there is no template library, these are equivalent
mb[mb$method != 'majvote',]$templates = mb[mb$method != 'majvote',]$top_n  # top_n is number of templates used

all_data = merge(ma, mb, by=c("timestamp", "atlases", "batch", "label", "reg_method", "subject"))
all_data$k_diff = all_data$k.y - all_data$k.x 
method_labels <- list("Majority Vote" = "majvote", 
                      "NMI Vote" = "nmi", 
                      "Cross-correlation Vote" = "xcorr")
levels(all_data$method.y) <- method_labels
all_data       = merge(all_data, diagnoses)
remove(t_ma, a_ma, t_mb, a_mb, ma, mb)
@

\begin{figure}
<<ADN1-Xval-k_mean, cache=TRUE>>=
ggplot(all_data, aes(x=templates.y,y=k.y, colour=as.factor(atlases))) + 
  facet_grid(reg_method~method.y) + 
  #stat_summary(fun.y=mean,geom='line',
  #             aes(y=k.y)) + 
  stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "mean Kappa" )
@
  \caption{MAGeT brain mean kappa by atlas and template library size}
  \label{ADNI1_xval}
\end{figure}

\begin{figure}
<<ADN1-Xval-k_diff, cache=TRUE>>=

ggplot(subset(all_data, reg_method=="ANTS" & method.y=="Majority Vote"), 
       aes(x=templates.y, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  #stat_summary(fun.y=mean,geom='line',position="dodge",
  #             aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_smooth(method=lm, formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Increase in mean Kappa between MAGeT brain and multiatlas" ) 
  #coord_cartesian(ylim=c(0,0.07), xlim=c(0.5,10.5))
@
  \caption{Increase in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}

\begin{figure}
<<ADN1-Xval-k_diff-ANTS-20tmpls>>=
a_20_tmpls = subset(all_data, 
                      reg_method  == "ANTS" &
                      method.y    == "Majority Vote" &
                      templates.y == 20)
ggplot(a_20_tmpls, aes(x=factor(atlases))) +
  stat_summary(fun.y=mean,geom='point',size=3,colour="red",aes(y=k.x)) +
  stat_summary(fun.y=mean,geom='line',colour="red",aes(y=k.x,group=1)) +
  stat_summary(fun.y=mean,geom='point',size=3,colour="blue",aes(y=k.y)) +
  stat_summary(fun.y=mean,geom='line',colour="blue",aes(y=k.y,group=1)) +
  labs(x="Number of Atlases", y = "Kappa", 
       title="mean Kappa of MA and MAGeT brain (ANTS/20 templates) \nvs\natlas library size") +
  scale_colour_hue(name="Method") + 
  coord_cartesian(ylim=c(0.7,0.9))
  #theme(legend.justification=c(1,0), legend.position=c(1,0))
@
  \caption{Change in mean Kappa between multi-atlas and MAGeT brain using ANTS, 20 templates}
  \label{}
\end{figure}

\begin{figure}
<<ADN1-Xval-k-by-disease, cache=TRUE>>=
a_20_tmpls = subset(all_data, 
                      reg_method  == "ANTS" &
                      method.y    == "Majority Vote" &
                      templates.y == 20 &
                      atlases %in% c(1,9))
template_library = read.csv('data/a2a_ants/template_library_composition.csv')
template_library$subject = NULL
a_20_tmpls = merge(a_20_tmpls, template_library,
                   by.x=c('timestamp', 'templates.y'), 
                   by.y=c('timestamp', 'templates'))
ggplot(a_20_tmpls, aes(y=k.y, x=templates_CN,colour=DX)) +  # why does k.x look the same?
  facet_grid( . ~ atlases) + 
  geom_smooth(method='lm',fullrange=F)

@@

<<ADNI-src-volumes-prep,echo=F,cache=T>>=
yr1   = read.csv("data/ADNI_baseline_volumes/ADNI1_Complete_1Yr_1.5T_11_15_2012.csv")
mb    = read.csv("data/ADNI_baseline_volumes/ADNI1_1.5T_MAGeT_volumes.csv")
maper = read.csv("data/ADNI_baseline_volumes/MAPER_volumes.csv")
snt   = read.csv("data/ADNI_baseline_volumes/UCSFSNTVOL.csv")
ucsd  = read.csv("data/ADNI_baseline_volumes/UCSDVOL.csv")
fs    = read.csv("data/ADNI_baseline_volumes/UCSFFSX_02_15_12.csv")
fsl   = read.csv("data/ADNI_baseline_volumes/ADNI1_1.5T_FSLFIRST_volumes.csv", sep=';')

# recode VISCODE
viscode_levels = list("bl"=1,"bl"=2, "m06"=3,"m12"=4)
yr1$VISCODE <- as.factor(yr1$Visit)
levels(yr1$VISCODE) <-viscode_levels

yr1$Scaled_2 <- grepl("Scaled_2", yr1$Description)

#TODO: include Scaled_2? 
subjects = subset(yr1, VISCODE == 'bl' & Scaled_2 == FALSE)

@@

attach(combined)
vols = data.frame(RID = RID, VISCODE = VISCODE, DX = DX.bl,
                  MAGeT = MAGeT_L + MAGeT_R, 
                  MAPER = MAPER_L + MAPER_R, 
                  SNT   = SNT_L + SNT_R, 
                  UCSD  = UCSD_L + UCSD_R,
                  FS    = FS_L + FS_R, 
                  FSL   = FSL_L + FSL_R)
@

\begin{figure}[h]
<<ADNI-src-volumes-boxplot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-prep',cache=T>>=
totals = vols
qplot(DX,value,data=melt(totals,measure.vars=c("FS", "FSL","UCSD", "MAPER","MAGeT","SNT"),na.rm=T),
      colour=variable,geom="boxplot") + 
        xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")

@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-src-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
by_snt_volumes = melt(totals, measure.vars=c("FSL","MAPER","MAGeT", "FS", "UCSD"))
fsl=subset(by_snt_volumes, variable=="FSL")
maper=subset(by_snt_volumes, variable=="MAPER")
maget=subset(by_snt_volumes, variable=="MAGeT")
with(by_snt_volumes,
qplot(SNT,value,data=by_snt_volumes,
      colour=variable, geom="smooth", method="lm") + 
    geom_point() +
     geom_text(aes(
       label=paste("FSL       R=", round(cor(fsl$SNT,fsl$value, use="complete.obs"), 2), 
                   ", p<", round(as.double(t.test(fsl$SNT,fsl$value, paired=T)["p.value"]), 2)),
       x=1800,y=10000, hjust=0,size=2), data=data.frame()) + 
#     geom_text(aes(
#       label=paste("MAPER R=", round(cor(maper$SNT,maper$value, use="complete.obs"), 2), 
#                   ", p<", t.test(maper$SNT,maper$value, paired=T)["p.value"]), 
#       x=1800,y= 9500, hjust=0, size=2)) +
#     geom_text(aes(
#       label=paste("MAGeT  R=", round(cor(maget$SNT,maget$value, use="complete.obs"),2), 
#                   ", p<", t.test(maget$SNT,maget$value, paired=T)["p.value"]), 
#       x=1800,y= 9000, hjust=0, size=2)) +
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (Automatic Segmentation)"))
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer
  (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

@@

latex(format.df(rbind(dx, overall), dec=2),
      n.cgroup=c(1,5),cgroup=c("","Volume Correlation"),
      n.rgroup=c(4,1), file="", size="scriptsize", )

@@

\begin{figure}
<<FEP_volumes,echo=F,fig=T, fig.align='center',cache=T>>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv")
with(SZ_volumes,
qplot(Manual,MAGeT,data=SZ_volumes) + geom_smooth(method="lm") + 
   geom_text(aes(
       label=paste("r = ", round(cor(Manual,MAGeT, use="complete.obs"), 2), 
                   ", p <", round(as.numeric(t.test(Manual, MAGeT, paired=T)["p.value"]), 6))),
       x=7000,y=10000, hjust=0,vjust=-0.5,size=5,data=data.frame()) +
    xlab("Total Hippocampal Volume (Manual Segmentation)") + 
    ylab("Total Hippocampal Volume (MAGeT Segmentation)")
)
@
  \caption{{\bf First Episode Schizophrenic Patients.} Comparison of total
  HC volumes for MAGeT against manually rated Hippocampal volumes}
  \label{SZ_volumes}
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1 X-Validation Dataset Demographics Table
%
<<ADNI-Xval-demographics, echo=F, results="asis",cache=FALSE>>=
adni_69_RIDs = c(295,413,619,685,729,782,938,954,1018,1155,907,981,222,324,448,
                 546,553,572,602,610,814,1341,675,681,731,1130,41,68,70,101,
                 249,293,316,414,698,1206,1222,1339,751,1030,3,5,10,16,22,53,
                 168,183,241,1205,328,1095,991,213,159,337,343,642,753,1109,
                 1217,29,56,1188,1293,149,382,431,1202)
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 +
               MMSE, data = adnimerge, subset = VISCODE == 'bl' & RID %in%
               adni_69_RIDs, method = "reverse", test=FALSE, overall=TRUE)

@@

{\bf Atlas and template libary.} The Winterburn atlases were used as the atlas
library.  The template library consisted of 21 randomly selected images from the
ADNI1 data dataset (7 healthy, MCI and AD subjects). Clinical and demographic
data for the template library subjects are shown in Table
\ref{tab:ADNI1_scr_tmpllib_demographics}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1 X-Validation Dataset Demographics Table
%
<<ADNI1-scr-tmpllib-demographics, echo=F, results="asis",cache=FALSE>>=
scr_tmpllib_RIDs = c(0295, 0413, 0619, 0685, 0729, 0782, 0938, 0954, 1018, 1155,
                 0907, 0981, 0448, 0553, 0814, 1130, 0698, 1339, 1095, 0991,
                 0159)
tab <- summary(DX.bl ~ AGE + PTGENDER + PTEDUCAT + PTETHCAT + CDRSB + ADAS13 +
               MMSE, data = adnimerge, subset = VISCODE == 'bl' & RID %in%
               scr_tmpllib_RIDs, method = "reverse", test=FALSE, overall=TRUE)

latex(tab, landscape=FALSE, ctable=FALSE, file="", size="scriptsize",
      caption="ADNI1 Screening Template Library demographics", 
      title="tab:ADNI1_scr_tmpllib_demographics")
@
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%                                                                              %
% ADNI1 Screening Validation - results preparation                             %
%                                                                              %
<<ADN1-Xval-prep, include=FALSE, cache=TRUE>>=
# all data from the validation trials
t_data       = read.csv(gzfile('data/a2a_ants/results_2013_01_03.csv.gz'))
t_data       = subset(t_data, atlases %in% c(1,3,5,7,9))
a_data       = t_data[,] #read.csv(gzfile('data/a2a_tracc/results_2013_01_03.csv.gz'))
diagnoses    = read.csv('data/a2a_diagnoses.csv')

# simplifies the table
t_data$se    = NULL
t_data$sn    = NULL
t_data$j     = NULL
a_data$se    = NULL
a_data$sn    = NULL
a_data$j     = NULL

# add registration method column 
t_data       = cbind(t_data, reg_method = "ANIMAL")
a_data       = cbind(a_data, reg_method = "ANTS")

# separate MA majvote from MB so we can compute differences
t_ma = subset(t_data, approach=="multiatlas" & method=="majvote")
a_ma = subset(a_data, approach=="multiatlas" & method=="majvote")
t_mb = subset(t_data, approach=="mb")
a_mb = subset(a_data, approach=="mb")

ma = rbind(t_ma,a_ma)
mb = rbind(t_mb,a_mb)

# set up a few equivalences for multi-atlas, to make nomenclature simpler
ma$templates =  ma$atlases  # because no template library
mb[mb$method != 'majvote',]$templates = mb[mb$method != 'majvote',]$top_n

all_data = merge(ma, mb, by=c("timestamp", "atlases", "batch", "label", "reg_method", "subject"))
all_data$k_diff = all_data$k.y - all_data$k.x 
method_labels <- list("Majority Vote" = "majvote", 
                      "NMI Vote" = "nmi", 
                      "Cross-correlation Vote" = "xcorr")
levels(all_data$method.y) <- method_labels
all_data       = merge(all_data, diagnoses)
remove(t_ma, a_ma, t_mb, a_mb, ma, mb)
@
%                                                                              %
%                                                                              %

The

\begin{figure}
<<ADN1-Xval-k-mean, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(all_data, aes(x=templates.y,y=k.y, colour=as.factor(atlases))) + 
  facet_grid(reg_method~method.y) + 
  #stat_summary(fun.y=mean,geom='line',
  #             aes(y=k.y)) + 
  stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" )
@
  \caption{MAGeT brain mean DSC by atlas and template library size}
  \label{fig:ADNI1_xval-k_mean}
\end{figure}

\begin{figure}
<<ADN1-Xval-k-diff, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(subset(all_data, reg_method=="ANTS" & method.y=="Majority Vote"), 
       aes(x=templates.y, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  #stat_summary(fun.y=mean,geom='line',position="dodge",
  #             aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_smooth(method=lm, formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Increase in mean Kappa between MAGeT brain and multiatlas" ) 
  #coord_cartesian(ylim=c(0,0.07), xlim=c(0.5,10.5))
@
  \caption{Increase in mean Kappa between MAGeT brain and multi-atlas}
  \label{ADNI1_cross_validation_MA_difference}
\end{figure}

\begin{figure}
<<ADN1-Xval-k-diff-ANTS-20tmpls, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
a_20_tmpls = subset(all_data, 
                      reg_method  == "ANTS" &
                      method.y    == "Majority Vote" &
                      templates.y == 20)
ggplot(a_20_tmpls, aes(x=factor(atlases))) +
  stat_summary(fun.y=mean,geom='point',size=3,colour="red",aes(y=k.x)) +
  stat_summary(fun.y=mean,geom='line',colour="red",aes(y=k.x,group=1)) +
  stat_summary(fun.y=mean,geom='point',size=3,colour="blue",aes(y=k.y)) +
  stat_summary(fun.y=mean,geom='line',colour="blue",aes(y=k.y,group=1)) +
  labs(x="Number of Atlases", y = "Kappa", 
       title="mean Kappa of MA and MAGeT brain (ANTS/20 templates) \nvs\natlas library size") +
  scale_colour_hue(name="Method") + 
  coord_cartesian(ylim=c(0.7,0.9))
  #theme(legend.justification=c(1,0), legend.position=c(1,0))
@
  \caption{Change in mean Kappa between multi-atlas and MAGeT brain using ANTS, 20 templates}
  \label{}
\end{figure}

\begin{figure}
<<ADN1-Xval-k-by-disease, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
a_20_tmpls = subset(all_data, 
                      reg_method  == "ANTS" &
                      method.y    == "Majority Vote" &
                      templates.y == 20 &
                      atlases %in% c(1,9))
template_library = read.csv('data/a2a_ants/template_library_composition.csv')
template_library$subject = NULL
a_20_tmpls = merge(a_20_tmpls, template_library,
                   by.x=c('timestamp', 'templates.y'), 
                   by.y=c('timestamp', 'templates'))
ggplot(a_20_tmpls, aes(y=k.y, x=templates_CN,colour=DX)) +  # why does k.x look the same?
  facet_grid( . ~ atlases) + 
  geom_smooth(method='lm',fullrange=F)

@@

@@

<<ADNI-src-volumes-prep,echo=F,cache=T>>=
bl1.5T= read.csv("data/ADNI_baseline_volumes/ADNI1_Screening_1.5T_11_15_2012.csv")
bl3T  = read.csv("data/ADNI_baseline_volumes/ADNI1_Baseline_3T_11_15_2012.csv")
mb    = read.csv("data/ADNI_baseline_volumes/ADNI1_1.5T_MAGeT_volumes.csv")
maper = read.csv("data/ADNI_baseline_volumes/MAPER_volumes.csv")
snt   = read.csv("data/ADNI_baseline_volumes/UCSFSNTVOL.csv")
ucsd  = read.csv("data/ADNI_baseline_volumes/UCSDVOL.csv")
fs    = read.csv("data/ADNI_baseline_volumes/UCSFFSX_02_15_12.csv")
fsl   = read.csv("data/ADNI_baseline_volumes/ADNI1_1.5T_FSLFIRST_volumes.csv", sep=';')

# recode VISCODE
#viscode_levels = list("bl"=1,"bl"=2, "m06"=3,"m12"=4)
#yr1$VISCODE <- as.factor(yr1$Visit)
#levels(yr1$VISCODE) <-viscode_levels
bl1.5T$VISCODE <- 'bl'
bl1.5T$Scaled_2 <- grepl("Scaled_2", yr1$Description)

#TODO: include Scaled_2? 
subjects = bl1.5T

@@

attach(combined)
totals = data.frame(RID = RID, VISCODE = VISCODE, DX = DX.bl,
                  MAGeT = MAGeT_L + MAGeT_R, 
                  MAPER = MAPER_L + MAPER_R, 
                  SNT   = SNT_L + SNT_R, 
                  UCSD  = UCSD_L + UCSD_R,
                  FS    = FS_L + FS_R, 
                  FSL   = FSL_L + FSL_R)
detach(combined)
complete_totals = subset(totals, !is.na(SNT) & !is.na(FSL) & !is.na(FS) & !is.na(MAPER) & !is.na(MAGeT))
@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T>>=
qplot(DX,value,data=melt(complete_totals,measure.vars=c("FS", "FSL","UCSD", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      xlab("Diagnosis") + ylab("Total Hippocampal Volume (mm3)")
@
  \caption{Comparison of HC volumes by FreeSurfer (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-scr-volumes-boxplot}
\end{figure}

\begin{figure}[h]
<<ADNI-scr-histogram,dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
melted = melt(complete_totals, measure.vars=c( "SNT","FSL","FS","MAPER","MAGeT"))
ggplot(data=melted, aes(x=value)) + 
       geom_histogram(binwidth=250) +
       facet_grid( variable ~ DX) 
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer
  (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-scr-histogram}
\end{figure}

\begin{figure}[h]
<<ADNI-src-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
by_snt_volumes = melt(totals, measure.vars=c( "SNT","FSL","FS","MAPER","MAGeT"))

with(by_snt_volumes,
ggplot(data=by_snt_volumes, aes(x=value)) + geom_histogram(binwidth=250) +
    facet_grid( variable ~ DX) 
     )
#     geom_text(aes(
#       label=paste("MAPER R=", round(cor(maper$SNT,maper$value, use="complete.obs"), 2), 
#                   ", p<", t.test(maper$SNT,maper$value, paired=T)["p.value"]), 
#       x=1800,y= 9500, hjust=0, size=2)) +
#     geom_text(aes(
#       label=paste("MAGeT  R=", round(cor(maget$SNT,maget$value, use="complete.obs"),2), 
#                   ", p<", t.test(maget$SNT,maget$value, paired=T)["p.value"]), 
#       x=1800,y= 9000, hjust=0, size=2)) +
#   xlab("Total Hippocampal Volume (Manual Segmentation)") + 
#   ylab("Total Hippocampal Volume (Automatic Segmentation)")) 
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer
  (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

\begin{figure}[h]
<<ADNI-src-volumes-plot,echo=F,fig=T, fig.align='center',dependson='ADNI-baseline-volumes-boxplot',cache=T>>=
by_snt_volumes = melt(totals, measure.vars=c( "SNT","FSL","FS","MAPER","MAGeT"))

with(by_snt_volumes,
ggplot(data=by_snt_volumes, aes(x=value)) + geom_histogram(binwidth=250) +
    facet_grid( variable ~ DX) 
     )
#     geom_text(aes(
#       label=paste("MAPER R=", round(cor(maper$SNT,maper$value, use="complete.obs"), 2), 
#                   ", p<", t.test(maper$SNT,maper$value, paired=T)["p.value"]), 
#       x=1800,y= 9500, hjust=0, size=2)) +
#     geom_text(aes(
#       label=paste("MAGeT  R=", round(cor(maget$SNT,maget$value, use="complete.obs"),2), 
#                   ", p<", t.test(maget$SNT,maget$value, paired=T)["p.value"]), 
#       x=1800,y= 9000, hjust=0, size=2)) +
#   xlab("Total Hippocampal Volume (Manual Segmentation)") + 
#   ylab("Total Hippocampal Volume (Automatic Segmentation)")) 
@
  \caption{{\bf ADNI Baseline cohort.} Comparison of HC volumes by FreeSurfer
  (FSF), MAGeT brain (MAGeT), MAPER, and manual (SNT).}
  \label{ADNI-baseline-volumes-plot}
\end{figure}

@@

latex(format.df(rbind(dx, overall), dec=2),
      n.cgroup=c(1,5),cgroup=c("","Volume Correlation"),
      n.rgroup=c(4,1), file="", size="scriptsize")

@@

\begin{figure}
<<FEP-volumes,cache=T>>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv")
with(SZ_volumes,
qplot(Manual,MAGeT,data=SZ_volumes) + geom_smooth(method="lm") + 
#   geom_text(aes(
#       label=paste("r = ", round(cor(Manual,MAGeT, use="complete.obs"), 2), 
#                   ", p <", round(as.numeric(t.test(Manual, MAGeT, paired=T)["p.value"]), 6))),
#       x=7000,y=10000, hjust=0,vjust=-0.5,size=5,data=data.frame()) +
   xlab("Total Hippocampal Volume (Manual Segmentation)") + 
   ylab("Total Hippocampal Volume (MAGeT Segmentation)")
)
@
  \caption{{\bf First Episode Schizophrenic Patients.} Comparison of total
  HC volumes for MAGeT against manually rated Hippocampal volumes}
  \label{SZ_volumes}
\end{figure}

@@

<<WAval-vol-boxplot,cache=T>>=
# dirty dirty
data = subset(read.csv('data/WAval.csv'), file != 'anusha')
gold_0.3mm = subset(data, version == "gold_0.3mm")
gold_0.6mm = subset(data, version == "gold_0.6mm")
mb_bravo   = subset(data, version == "mb_bravo")
mb_0.6mm   = subset(data, version == "mb_0.6mm")

gold_0.3mm_total = gold_0.3mm[,2:6] + gold_0.3mm[,7:11]
gold_0.6mm_total = gold_0.6mm[,2:6] + gold_0.6mm[,7:11]
mb_bravo_total   = mb_bravo[,2:6] + mb_bravo[,7:11]
mb_0.6mm_total   = mb_0.6mm[,2:6] + mb_0.6mm[,7:11]

gold_diff     = (gold_0.3mm_total - gold_0.6mm_total)/gold_0.3mm_total
mb_bravo_diff = (gold_0.3mm_total - mb_bravo_total)/gold_0.3mm_total
mb_0.6mm_diff = (gold_0.3mm_total - mb_0.6mm_total)/gold_0.3mm_total

subjects = gold_0.6mm[,1]
mb0.6mm_diff_over_gold_diff = cbind(subjects, mb_0.6mm_diff - mean(gold_diff) , res="diffdff")
gold_diff     = cbind(subjects,gold_diff, res="0.3mm gold & 0.6mm gold")
mb_bravo_diff = cbind(subjects,mb_bravo_diff, res="0.3mm gold & MAGeT-on-BRAVO")
mb_0.6mm_diff = cbind(subjects,mb_0.6mm_diff, res="0.3mm gold & MAGeT-at-0.6mm")

diff = rbind(mb_bravo_diff,mb_0.6mm_diff,gold_diff, mb0.6mm_diff_over_gold_diff)
names(diff) <- c("subject", "CA1", "Subiculum", "CA4", "CA2/CA3", "Dentate", "res")

melted = melt(diff, id.vars=c("subject", "res"))
names(melted) <- c("subject","res", "region","voldiff")
ggplot(melted, aes(y=voldiff,x=region)) +
  geom_boxplot() + facet_grid( . ~ res)  + 
  labs(title="Percent difference in MAGeT volumes from original",
       y="Percent difference in volume", 
       x="Region") 
@

<<WAval-kappa,cache=T>>=
data = read.csv('data/WAval-kappa.csv')
ggplot(data, aes(x=label, y=kappa)) + geom_boxplot(y=kappa)
@
